A Review of Lossless Data Compression Methods

### 2018-11-15 paper.tex
Progress on paper lol

\usepackage{graphicx}
\usepackage{amssymb, amsmath, amsthm, amsfonts}
\usepackage{tikz}
\usepackage[pdfusetitle]{hyperref}

@@

This result places a lower bound on the \emph{efficiency} of prefix
codes in general, and suggests the sorts of data which are less
compressable, and even uncompressable (since such an input must
exist!) Since entropy of some channel $X$ with an alphabet $C$ is
defined to be $H(X) = -\sum_{c \in C} P(c)\log_2{c}$, we can
illustrate the implications of this result with a simple
example. Clearly for a channel using binary alphabet (i.e.,
$C = \{0, 1\}$) with a uniform distribution of 1s and 0s, the entropy
of this channel is $H(X) = -2 * \frac{1}{2}\log_2{\frac{1}{2}} = 1$,
so some optimal prefix code must have an average word length greater
than or equal to 1; obviously, the simplest prefix code to encode
$\{0, 1\}$ is $\{0, 1\}$ itself. Thus, a this channel is
incompressible.

@@

The Lempel-Ziv compression algorithm, or simply LZ for short, is one
of the most widespread compression schemes in use, when including its
large family of derivative methods. It was first introduced in 1977 in
\cite{LempelZiv}.

@@

\bibliography{biblio}{}
\bibliographystyle{plain}

>>>>

\usepackage{graphicx}
\usepackage{amssymb, amsmath, amsthm, amsfonts}
\usepackage{tikz}
\usepackage[pdfusetitle]{hyperref}
\usepackage{apacite}

@@

This result places a lower bound on the \emph{efficiency} of prefix
codes in general, and suggests the sorts of data which are less
compressable, and even uncompressable (since such an input must
exist!) Since entropy of some channel $X$ with an alphabet $C$ is
defined to be $H(X) = -\sum_{c \in C} P(c)\log_2{c}$, we can
illustrate the implications of this result with a simple
example. Suppose we are attempting to compress a particular channel
$X$ which is text document in which the frequencies of every letter of
the Latin alphabet are distributed equally. (It is extremely unlikely
that a text in any human language would have this property; it is used
here to illustrate a pathological edge case in general.) Then the
average word length must be greater than
$26 * -\frac{1}{26} \log_2{\frac{1}{26}} \approx 4.7$ bits. If we were
to construct a naive code to encode the Latin alphabet, for instance
$A=1, B=2,...$, we would require 5 bits for each letter. Shannon's
Noiseless Coding Theorem says this is more or less as good as we can
do, so for this case it is very difficult to actually compress our
input. Consider another document in which case one letter, let's say
$E$, occurs significantly more often than the others, for instance
$\frac{27}{52}$ of the time, relative to $\frac{1}{52}$ for every
other letter. Then by Shannon's Noiseless Coding Theorem, it is
possible to construct a code with an average word length greater than
$25 * -\frac{1}{52} \log_2{\frac{1}{52}} - \frac{27}{52}
\log_2{\frac{27}{25}} \approx 3.2$, meaning that we can compress such
this document approximately $33\%$ more efficiently than the uniform
one. This situation is somewhat contrived, but it serves to illustrate
the fundamental limits of prefix codes in general.

@@

The Lempel-Ziv compression algorithm, commonly referred to as LZ for
short, is one of the most widespread compression schemes in use,
especially when including its large family of derivative methods. It
was first introduced in 1977. \cite{LempelZiv} Algorithms based on
the Lempel-Ziv algorithms are very efficient and work well with a wide
variety of inputs.

@@

\bibliographystyle{apacite}
\bibliography{biblio}
